---
title: 'CGPBox Pipeline'
author: '---'
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
---  


```{r include = FALSE}
require(rmarkdown); require(knitr);

options(max.print = "99", knitr.duplicate.label = 'allow'); opts_knit$set(width = 99)
opts_chunk$set(cache=FALSE, tidy=FALSE)

```

https://github.com/cancerit/cgpbox

This is a repacking of the cgpbox pipeline to allow for parellization via the rabix executor and descriptions of the tools included by commmon workflow language.

<br><br>

# 1. CGP Bam Stats {.tabset .tabset-fade .tabset-tabs}

```{r child = '~/cgpbox-cwl/Rmarkdown/bam_stats/bam_stats.Rmd'}


```

# 2. CGP Genotype Check {.tabset .tabset-fade .tabset-tabs}

```{r child = '~/cgpbox-cwl/Rmarkdown/genotype_check/genotype_check.Rmd'}


```

# 3. Verify Bams {.tabset .tabset-fade .tabset-tabs}

```{r child = '~/cgpbox-cwl/Rmarkdown/verify_bams/verify_bams.Rmd'}


```

# 4. ASCAT {.tabset .tabset-fade .tabset-tabs}

```{r child = '~/cgpbox-cwl/Rmarkdown/ascat/ascat.Rmd'}


```

# 5. CGP Pindel {.tabset .tabset-fade .tabset-tabs}

```{r child = '~/cgpbox-cwl/Rmarkdown/pindel/pindel.Rmd'}


```

# 6. CaVEMan {.tabset .tabset-fade .tabset-tabs}

```{r child = '~/cgpbox-cwl/Rmarkdown/caveman/caveman.Rmd'}


```

# 7. Brass {.tabset .tabset-fade .tabset-tabs}

```{r child = '~/cgpbox-cwl/Rmarkdown/brass/brass.Rmd'}


```

# 8. CGP Annotate VCF {.tabset .tabset-fade .tabset-tabs}

```{r child = '~/cgpbox-cwl/Rmarkdown/cgp_annotate_vcf/cgp_annotate_vcf.Rmd'}


```

